%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    % \textbf{#1}{: #2 \vspace{-2pt}}
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://ryanefendy.com/}{\Large Ryan Efendy}} & Email : \href{mailto:ryanefendy95@gmail.com}{ryanefendy95@gmail.com}\\
  \href{https://ryanefendy.com/}{https://ryanefendy.com/} & Mobile : +1-267-307-3323 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Master of Science in Computer Science;  GPA: 4.00}{Jan. 2019 -- Present}
    \resumeSubheading
      {Drexel University}{Philadelphia, PA}
      {Bachelor of Science in Computer Science;  GPA: 3.40}{Sept. 2013 -- Jun. 2018}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Microsoft}{Redmond, WA}
      {Software Engineer}{Jul. 2018 - Present}
      \resumeItemListStart
        \resumeItem{}
          {Upgraded and migrated more than \textbf{10} directives in AngularJS to Angular components}
        \resumeItem{}
          {Proposed and implemented a redesigned state container with NgRx with better predictability and performance in Angular application}
        \resumeItem{}
          {Performed daily performance, reliability, and failure monitoring tasks to ensure proper health of multiple services}
      \resumeItemListEnd
      
    \resumeSubheading
      {Product School}{Seattle, WA}
      {Coding Boot Camp Instructor}{Sept. 2018 - Nov. 2018}
      \resumeItemListStart
        \resumeItem{}
          {Taught \textbf{10+} students full-stack web development, cutting-edge technologies and best practices through lectures and building applications}
      \resumeItemListEnd

    \resumeSubheading
      {Amazon}{New York City, NY}
      {Software Engineer}{Sept. 2017 - Dec. 2017}
      \resumeItemListStart
        \resumeItem{}
          {Developed an automated End-to-End Testing framework for Jupyter Notebook using Nightwatch.js and Selenium}
        \resumeItem{}
          {Created a Python library and Node.js module to parse Docker configuration files to retrieve Amazon ECR Registries URI}
        \resumeItem{}
          {Configured AWS Batch’s job definition, compute environment, and job queue to encode files from csv to protobuf format}
      \resumeItemListEnd
      
    \resumeSubheading
      {PayPal}{Scottsdale, AZ}
      {Site Reliability Engineer}{Jun. 2017 - Sept. 2017}
      \resumeItemListStart
        \resumeItem{}
          {Implemented form components to collect user input to be passed to a Node.js, Express and MongoDB backend to triage tickets based on priority level and make appropriate decisions}
        \resumeItem{}
          {Developed new features using React and Redux and built reusable components and front-end libraries for future use such as input components that are shared in more than \textbf{10} pages of the applications}
        \resumeItem{}
          {Refactored Grunt build tasks to decrease build times from \textbf{30} seconds to less than \textbf{5} seconds in a React, Node project by separating the tasks and enabled live reloading of updated files to the browser}
      \resumeItemListEnd
      
    \resumeSubheading
      {Oracle}{Conshohocken, PA}
      {Applications Engineer}{Jun. 2016 - Jun. 2017}
      \resumeItemListStart
        \resumeItem{}
          {Implemented multiple Quick Filters in more than 3 pages of Primavera Prime application to allow users quickly filter attributes to only see specific items, utilized internal JavaScript libraries and wrote QUnit tests with a testing coverage of over \textbf{90\%}}
        \resumeItem{}
          {Wrote \textbf{2000} lines of Qunit and \textbf{1000} lines of JUnit/integration testing code which increased testing coverage by \textbf{25\%} span across \textbf{10} different pages of Primavera Prime application}
        \resumeItem{}
          {Fixed \textbf{20+} bugs and defects of level \textbf{3} and \textbf{4} severity, medium priority and added test cases to prevent the bugs and defects from breaking again in the future}
      \resumeItemListEnd
      
    \resumeSubheading
      {J.P. Morgan}{Wilmington, DE}
      {Software Engineer}{Mar. 2016 - Jun. 2016}
      \resumeItemListStart
        \resumeItem{}
          {Refactored \textbf{5+} VBA scripts to Python scripts to manipulate data following specifications and requirements using pandas and XlsxWriter}
      \resumeItemListEnd
      
    \resumeSubheading
      {Comcast}{Mount Laurel, NJ}
      {Software Engineer}{Mar. 2015 - Sept. 2015}
      \resumeItemListStart
        \resumeItem{}
          {Implemented Python scripts to send HTML-formatted email using Gmail’s SMTP service to \textbf{20+} clients}
      \resumeItemListEnd



  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{}
      {\textbf{Lyft Offline (1st place Pennapps XIV: Best Use of Lyft API)}: Enable user to request a Lyft with NO Internet connection only through SMS}
    \resumeSubItem{}
      {\textbf{HarassBlocker Plus (1st place Medhacks 2.0: Hack Harassment)}: Content filtering service which uses IBM Watson and neural networks to detect harassing content}
    \resumeSubItem{}
      {\textbf{EmotiBoo (1st place DubHacks: Best Use of Data Visualization with Qualtrics)}: Aid people with social communication disorders by displaying the emotions of the speaker in a concise way}
    \resumeSubItem{}
      {\textbf{WorldChat (DragonHacks: Winner of Globo's  Challenge)}: Ask all your questions to real people and have them answered in real time in your own language}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
